Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-07-20 Paper/Poster/poster.tex
new figs
nyu logo added

%%% Unisiegel
\begin{minipage}[c][10cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{labrosa-logo.eps}
  \end{center}
\end{minipage}
%%% Title
\begin{minipage}[c][9cm][c]{0.78\textwidth}
  \begin{center}
    {\sc \Huge Clustering Beat-Chroma Patterns}\\[5mm]
  {\sc \Huge in a Large Music Database}\\[10mm]
    {\Large Thierry Bertin-Mahieux $^\dagger$, Ron J. Weiss $^\ddagger$ and Daniel P. W. Ellis $^\dagger$\\[3.5mm]
     \large $\dagger$ LabROSA, Dept. of Electrical Engineering, Columbia University \\
     \large $\ddagger$ MARL, New York University \\
    \tt{\{thierry,ronw,dpwe\}@ee.columbia.edu}}
  \end{center}
\end{minipage}
%%% GK-Logo
\begin{minipage}[c][9cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
  \end{center}
\end{minipage}

@@

@@

>>>>

%%% Unisiegel
\begin{minipage}[c][10cm][c]{0.2\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{labrosa-logo.eps} \\
    \vspace{1cm}
    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
  \end{center}
\end{minipage}
%\begin{minipage}[c][9cm][c]{0.1\textwidth}
%  \begin{center}
%    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
%  \end{center}
%\end{minipage}
%%% Title
\begin{minipage}[c][9cm][c]{0.58\textwidth}
  \begin{center}
    {\sc \Huge Clustering Beat-Chroma Patterns}\\[5mm]
  {\sc \Huge in a Large Music Database}\\[10mm]
    {\Large Thierry Bertin-Mahieux $^\dagger$, Ron J. Weiss $^\ddagger$ and Daniel P. W. Ellis $^\dagger$\\[3.5mm]
     \large $\dagger$ LabROSA, Dept. of Electrical Engineering, Columbia University \\
     \large $\ddagger$ MARL, New York University \\
    \tt{\{thierry,ronw,dpwe\}@ee.columbia.edu}}
  \end{center}
\end{minipage}
%%% GK-Logo
\begin{minipage}[c][7cm][c]{0.2\textwidth}
  \begin{center}
    \includegraphics[width=10cm,angle=0]{MARL_logo_high_res.eps} \\
    \vspace{1.5cm}
    \includegraphics[width=8cm,angle=0]{nyu_music_tech_logo_2_2_bw.eps}
  \end{center}
\end{minipage}

@@

\myfig[0]{song_encoded.ps}{.9}

\myfig[0]{codes_8bars.ps}{.8}

@@

Boring graphs on distortion, codeword size, etc, can be seen in the paper.

\myfig[0]{codes1.ps}{.8}

\myfig[0]{close_patterns1.ps}{.8}

\myfig[0]{close_patterns_diff.ps}{.8}

\myfig[0]{codes_lle.ps}{.8}
